### 2025-01-11 sections/4-results.tex
added legends

\begin{figure}
    \captionsetup[subfigure]{aboveskip=-15pt,belowskip=-3pt}
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{images/lfd/fashion-mnist.png}\\
        \subcaption{Fashion-mnist}
        \label{fig:results:fashion-mnist-lfd}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{images/lfd/glove-25.png}\\
        \subcaption{Glove-25}
        \label{fig:results:glove-25-lfd}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{images/lfd/sift.png}\\
        \subcaption{Sift}
        \label{fig:results:sift-lfd}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{images/lfd/random.png}\\
        \subcaption{A random dataset}
        \label{fig:results:random-lfd}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{images/lfd/silva-SSU-Ref.png}\\
        \subcaption{Silva 18S}
        \label{fig:results:silva-lfd}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{images/lfd/radio-ml.png}\\
        \subcaption{RadioML}
        \label{fig:results:radioml-lfd}
    \end{subfigure}%
    \caption{Local fractal dimension vs. cluster depth across six datasets, grouped by percentiles of local fractal dimension and weighted by the cardinalities of the clusters.}
    \label{fig:results:lfd-plots}
\end{figure}

@@

\begin{figure}
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{plots/fashion-mnist_PermutedBall_10_throughput.png}
        \subcaption{Fashion-Mnist for $k=10$.}
        \label{fig:results:fashion-mnist-scaling}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{plots/glove-25_PermutedBall_10_throughput.png}
        \subcaption{Glove-25 for $k=10$.}
        \label{fig:results:glove-25-scaling}
    \end{subfigure}%
    \\
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{plots/sift_PermutedBall_10_throughput.png}
        \subcaption{Sift for $k=10$.}
        \label{fig:results:sift-scaling}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{plots/random_PermutedBall_10_throughput.png}
        \subcaption{A random dataset for $k=10$.}
        \label{fig:results:random-scaling}
    \end{subfigure}%
    \\
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{plots/silva-SSU-Ref_PermutedBall_10_throughput.png}
        \subcaption{Silva for $k=10$.}
        \label{fig:results:silva-scaling}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{plots/radio-ml_Ball_10_throughput.png}
        \subcaption{RadioML for $k=10$ at SnR = 10dB.}
        \label{fig:results:radioml-scaling}
    \end{subfigure}%
    \caption{Throughput across six datasets, including a randomly-generated dataset.
    In each plot, the horizontal axis represents increasing cardinality of the dataset, while the vertical axis represents the throughput in queries per second (higher is better).
    For HNSW and ANNOY, we were not able to take measurements for each cardinality because building the index required more RAM than was available (i.e.,\,more then 512GB).
    For linear search with CAKES, we only report the throughput for a few of the initial multipliers because the trend is clear.}
    \label{fig:results:scaling-plots}
\end{figure}

\begin{figure}
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{images/distance_counts/fashion-mnist_KnnRepeatedRnn_10_throughput.png}
        \subcaption{Repeated $\rho$-NN}
        \label{fig:results:fashion-mnist-counts-throughput}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{images/distance_counts/fashion-mnist_KnnRepeatedRnn_10_counts.png}
        \subcaption{Repeated $\rho$-NN}
        \label{fig:results:glove-25-counts-counts}
    \end{subfigure}%
    \\
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{images/distance_counts/fashion-mnist_KnnBreadthFirst_10_throughput.png}
        \subcaption{Breadth First Sieve}
        \label{fig:results:sift-counts-throughput}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{images/distance_counts/fashion-mnist_KnnBreadthFirst_10_counts.png}
        \subcaption{Breadth First Sieve}
        \label{fig:results:random-counts-counts}
    \end{subfigure}%
    \\
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{images/distance_counts/fashion-mnist_KnnDepthFirst_10_throughput.png}
        \subcaption{Depth First Sieve}
        \label{fig:results:silva-counts-throughput}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{images/distance_counts/fashion-mnist_KnnDepthFirst_10_counts.png}
        \subcaption{Depth First Sieve}
        \label{fig:results:radioml-counts-counts}
    \end{subfigure}%
    \caption{Number of distance computations across four clustering strategies and three search algorithms on the Fashion-Mnist dataset.
    Adding the instrumentation to count the number of distance computations had the side-effect of significantly slowing down the search algorithms compared to those reported in Figure~\ref{fig:results:scaling-plots}.
    The left column shows the throughput in queries per second, while the right column shows the mean number of distance computations per query.
    The x-axis represents increasing cardinality of the dataset.}
    \label{fig:results:distance-counts}
\end{figure}

>>>>

\begin{figure}
    \captionsetup[subfigure]{aboveskip=-15pt,belowskip=-3pt}
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.9\textwidth]{images/lfd/fashion-mnist.png}\\
        \subcaption{Fashion-mnist}
        \label{fig:results:fashion-mnist-lfd}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.9\textwidth]{images/lfd/glove-25.png}\\
        \subcaption{Glove-25}
        \label{fig:results:glove-25-lfd}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.9\textwidth]{images/lfd/sift.png}\\
        \subcaption{Sift}
        \label{fig:results:sift-lfd}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.9\textwidth]{images/lfd/random.png}\\
        \subcaption{A random dataset}
        \label{fig:results:random-lfd}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.9\textwidth]{images/lfd/silva-SSU-Ref.png}\\
        \subcaption{Silva 18S}
        \label{fig:results:silva-lfd}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.9\textwidth]{images/lfd/radio-ml.png}\\
        \subcaption{RadioML}
        \label{fig:results:radioml-lfd}
    \end{subfigure}%
    \\
    \vskip 0.005in
    \begin{subfigure}[b]{0.94\textwidth}
        \centering
        \includegraphics[width=0.7\textwidth]{images/lfd/legend.png}
        \label{fig:results:lfd-legend}
    \end{subfigure}%
    \caption{Local fractal dimension vs. cluster depth across six datasets, grouped by percentiles of local fractal dimension and weighted by the cardinalities of the clusters.
    Note that the y-axis is different for the random dataset.}
    \label{fig:results:lfd-plots}
\end{figure}

@@

\begin{figure}
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=1.0\textwidth]{plots/fashion-mnist_PermutedBall_10_throughput.png}
        \subcaption{Fashion-Mnist for $k=10$.}
        \label{fig:results:fashion-mnist-scaling}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=1.0\textwidth]{plots/glove-25_PermutedBall_10_throughput.png}
        \subcaption{Glove-25 for $k=10$.}
        \label{fig:results:glove-25-scaling}
    \end{subfigure}%
    \\
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=1.0\textwidth]{plots/sift_PermutedBall_10_throughput.png}
        \subcaption{Sift for $k=10$.}
        \label{fig:results:sift-scaling}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=1.0\textwidth]{plots/random_PermutedBall_10_throughput.png}
        \subcaption{A random dataset for $k=10$.}
        \label{fig:results:random-scaling}
    \end{subfigure}%
    \\
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=1.0\textwidth]{plots/silva-SSU-Ref_PermutedBall_10_throughput.png}
        \subcaption{Silva for $k=10$.}
        \label{fig:results:silva-scaling}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=1.0\textwidth]{plots/radio-ml_Ball_10_throughput.png}
        \subcaption{RadioML for $k=10$ at SnR = 10dB.}
        \label{fig:results:radioml-scaling}
    \end{subfigure}%
    \\
    \begin{subfigure}[b]{0.94\textwidth}
        \centering
        \includegraphics[width=0.7\textwidth]{plots/legend.png}
        \label{fig:results:scaling-legend}
    \end{subfigure}%
    \caption{Throughput across six datasets, including a randomly-generated dataset.
    In each plot, the horizontal axis represents increasing cardinality of the dataset, while the vertical axis represents the throughput in queries per second (higher is better).
    For HNSW and ANNOY, we were not able to take measurements for each cardinality because building the index required more RAM than was available (i.e.,\,more then 512GB).
    For linear search with CAKES, we only report the throughput for a few of the initial multipliers because the trend is clear.}
    \label{fig:results:scaling-plots}
\end{figure}

\begin{figure}
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=1.0\textwidth]{images/distance_counts/fashion-mnist_KnnRepeatedRnn_10_throughput.png}
        \subcaption{Repeated $\rho$-NN}
        \label{fig:results:fashion-mnist-counts-throughput}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=1.0\textwidth]{images/distance_counts/fashion-mnist_KnnRepeatedRnn_10_counts.png}
        \subcaption{Repeated $\rho$-NN}
        \label{fig:results:glove-25-counts-counts}
    \end{subfigure}%
    \\
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=1.0\textwidth]{images/distance_counts/fashion-mnist_KnnBreadthFirst_10_throughput.png}
        \subcaption{Breadth First Sieve}
        \label{fig:results:sift-counts-throughput}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=1.0\textwidth]{images/distance_counts/fashion-mnist_KnnBreadthFirst_10_counts.png}
        \subcaption{Breadth First Sieve}
        \label{fig:results:random-counts-counts}
    \end{subfigure}%
    \\
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=1.0\textwidth]{images/distance_counts/fashion-mnist_KnnDepthFirst_10_throughput.png}
        \subcaption{Depth First Sieve}
        \label{fig:results:silva-counts-throughput}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=1.0\textwidth]{images/distance_counts/fashion-mnist_KnnDepthFirst_10_counts.png}
        \subcaption{Depth First Sieve}
        \label{fig:results:radioml-counts-counts}
    \end{subfigure}%
    \\
    \begin{subfigure}[b]{0.94\textwidth}
        \centering
        \includegraphics[width=0.6\textwidth]{images/distance_counts/legend.png}
        \label{fig:results:counts-legend}
    \end{subfigure}%
    \caption{Number of distance computations across four clustering strategies and three search algorithms on the Fashion-Mnist dataset.
    Adding the instrumentation to count the number of distance computations had the side-effect of significantly slowing down the search algorithms compared to those reported in Figure~\ref{fig:results:scaling-plots}.
    The left column shows the throughput in queries per second, while the right column shows the mean number of distance computations per query.
    The x-axis represents increasing cardinality of the dataset.}
    \label{fig:results:distance-counts}
\end{figure}
